---
title: "CodeBook"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This script will import specific files, extract columns with a specific mean, merge both test and training files plus generate the mean for those columns for each individual (ind)..

## Including Code

You can include R code in the document as follows:

#load 4 files, file1 & file3 are data,file2 & file4 are the individual (i.e. labels foreach row)
file1 = read.table("./zipFile/test/X_test.txt", header = FALSE)
file2 = read.table("./zipfile/test/y_test.txt")

file3 = read.table("./zipFile/train/X_train.txt", header = FALSE)
file4 = read.table("./zipFile/train/y_train.txt")

#add the column headers from file features.txt to file 1 & 3
column_names = read.table("./zipFile/features.txt")
CL_name1 = column_names[,2] # row the column list of names i.e column 2
#CL_name1
#class(CL_name1)
colnames(file1) <-CL_name1
#write.csv(file1,"./ZipFile/file1_names.csv")
colnames(file3) <-CL_name1
#write.csv(file3, "./ZipFile/file3_names.csv")

#add the column header to file 2 & 4 "individual
colnames(file2) <-"individual"
#head(file2)
#write.csv(file2,"./ZipFile/file2_names.csv")
colnames(file4) <-"individual"
#write.csv(file4, "./zipFile/file4_names.csv")

#add the row titles to file 1 & 3 with the information in file 2 & 4
mergeData1 <- merge(file2,file1,by="row.names", sort = FALSE)
#write.csv(mergeData1, "./zipFile/mergedata1.csv")
mergeData2 <- merge(file4,file3, by="row.names", sort = FALSE)
#write.csv(mergeData2,"./zipFile/mergeData2.csv")

#merge the test and training sets
mergeData <- merge(mergeData1, mergeData2,all = TRUE, sort = FALSE)
write.csv(mergeData,"./zipFile/mergedata.csv")

#make individual names for the larger file
Ind <- mergeData[,2]
#write.csv(Ind,"./zipFile/Ind.csv")
# can I delete this????write.csv(mergeInd,"./zipFile/mergeInd.csv")

#subset columns based on key word mean, i.e. take out all columns containing the word column
subset1 <- mergeData[,grep("mean",colnames(mergeData))]
#droplevels.data.frame(subset1)
#write.csv(subset1, "./zipFile/subset1.csv")

subset2 <- mergeData[,grep("std",colnames(mergeData))]
#droplevels.data.frame(subset2)
#write.csv(subset2, "./zipFile/subset2.csv")

#combine the subset and add individual names to them
mean_std_set <- cbind(Ind,subset1,subset2)
write.csv(mean_std_set, "./zipFile/Data_set_step4")


require(data.table)
DT <-data.table(mean_std_set)
#write.csv(DT,"./zipFile/DT.csv")
Ind_mean <-DT[,lapply(.SD, mean), by = mean_std_set$Ind]
write.csv(Ind_mean, "./zipFile/Data_set-step4_mean_std.csv") 

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
